---
title: "Data Overview"
author: 
date: 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(knitr)


```

  This is NFL Data that I have broken down to recieving data for Julian Edelman on the New England Patriots. I would like to explore how Julian Edelman's success has evolved over time and if he has progressed or if his situation improved resulting in his improvement. 

  Through his first 4 seasons he only averaged, at most 4 targets a game, but since 2013 he has averaged at least 9 targets/game demonstrating progression and potentially an improved confidence from Brady. However, it is important to note that in 2012 Wes Welker, the Patriots leading reciever, left the team. The same results are apparent with yardage, his yardage spiked in 2013 by about 40 yards/game.

  In terms of how he fares against certain opponents, on average his top 5 most favorable matchups are DAL, LA, SD, SEA, and DET. His closest divisional oponent is MIA at 73 yards/game, with no other divisional opponents in tops 10.
  
  In conclusion, it seems that Edelman filled the void that Welker left in 2012. In other words, Edelman's improved production, I believe, is a product of his new role in the Patriots system after Welker left.



```{r, include=FALSE, echo=FALSE}


Jules <- read_csv("legacy_data/game_player_stats/game_receiving_df.csv") %>%
  filter(Team == "NE") %>%
  filter(Player_Name == "J.Edelman") 

#This is NFL Data that I have broken down to recieving data for Julian Edelman on the New England Patriots. I would like to explore something that involves how Julian Edelman's success effects the succes of the team as a whole. 
```


```{r, include=FALSE, echo=FALSE}
summary(Jules)
```

#Average Targets/Game by Season Progression
```{r, echo=FALSE}
Jules %>%
  mutate(Season = str_sub(GameID, 1, 4)) %>%
  group_by(Season) %>%
  summarize(Avg_Targets = mean(Targets)) %>%
  kable()

#through his first 4 seasons he only averaged, at most 4 targets a game, but since 2013 he has averaged at least 9 targets/game demonstrating progression and potentially an improved confidence from Brady
```



#Average Yards/Game by Season Progression
```{r, echo=FALSE}
Jules %>%
  mutate(Season = str_sub(GameID, 1, 4)) %>%
  group_by(Season) %>%
  summarize(Avg_Yards = mean(Total_Yards)) %>%
  kable()

#same as with targets, his yardage spiked in 2013 by ~ 40 yards/game

```

#Average Yards/Game by Opponent
```{r, echo=FALSE}
Jules %>%
  group_by(Opponent) %>%
  summarize(Avg_Yards = mean(Total_Yards)) %>%
  filter(Avg_Yards >= 70) %>%
  kable()


#On Avg his top 5 most favorable matchups are DAL, LA, SD, SEA, and DET
#His closest divisional oponent is MIA at 73 yards/game, No other divisional opponents in tops 10
```

